\documentclass[letterpaper,12pt]{article}

\usepackage{url}
\usepackage{parskip} 	

\RequirePackage{color}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}

\newcolumntype{C}{>{\centering\arraybackslash}X} 
\usepackage{titlesec}				

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

\usepackage{fontawesome5}

\begin{document}
\pagestyle{empty} 

\begin{tabularx}{\linewidth}{@{} C @{}}
{\Huge{Zicheng Li}}  {\small{Hamilton, ON}} \\\\ 
\href{https://github.com/Zicheng-Li}{\raisebox{-0.05\height}\faGithub\ Zicheng-Li} \ $|$ \ 
\href{https://www.linkedin.com/in/zicheng-li-873078256/}{\raisebox{-0.05\height}\faLinkedin\ zicheng-li} \ $|$ \ 
\href{https://www.zicheng-li.com/}{\raisebox{-0.05\height}\faGlobe \ zicheng-li.com} \ $|$ \ 
\href{mailto:li1276@mcmaster.ca}{\raisebox{-0.05\height}\faEnvelope \ li1276@mcmaster.ca} \\ 
% \href{tel:+13063618126}{\raisebox{-0.05\height}\faMobile \ (+1) 306-361-8126} \\
\end{tabularx}

% \section{Profile}
% As a university student, I am a fast and effective learner with strong problem-solving abilities. Additionally, I possess strong communication skills. I am actively seeking opportunities to gain experience in the computer science field.

\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
\textbf{Bachelor of Applied Science (BASc), Computer Science} &  \hfill \normalsize{Sep 2021 - April 2025} \\

McMaster University &  \hfill Hamilton, Canada \\
\end{tabularx}

\hspace{0.3cm} $\bullet$ {\fontsize{10pt}{9pt}\selectfont Obtained a 3.9/4.0 GPA in all ten courses completed during the first year of study.}

\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
% \textbf{Technical Skills}  &  \normalsize{} \\
Languages: \hspace{0.4cm} HTML   \hspace{0.6cm}   CSS \hspace{0.6cm} JavaScript \hspace{0.6cm} Java \hspace{0.6cm} Python \hspace{0.6cm} C \hspace{0.6cm} SQL \hspace{0.6cm} Latex \\
Frameworks: \hspace{0.13cm} Linux \hspace{0.7cm} AWS Cloud 
\end{tabularx}

% \textbf{Soft Skills}\\
% Problem Solving Skills \hspace{0.8cm} Communication Skills \hspace{0.8cm} Multitasking Skills \hspace{0.8cm} Time management skills

% \hspace{0.1cm} $\bullet$ \hspace{0.2cm}{\fontsize{10pt}{9pt}\selectfont I possess strong communication skills and problem-solving abilities. During Deltahacks 9, I effectively communicated with my team members and carefully analyzed our topic, successfully solving technical challenges and completing our project. Additionally, as a speaker, I presented our project to the judges.}

\section{Projects}

\textbf{Math Assistant (DeltaHacks 9 Project)} \hfill \href{https://devpost.com/software/math-helper-graphing-calculator}{Link to Demo} \hspace{0.2cm} \href{https://github.com/Zicheng-Li/Math_helper}{Link to GitHub} \\
\textit{January, 2023} \\ 
\hspace{0.1cm} $\bullet$\hspace{0.11cm} Successfully developed a graphing calculator called ``Math Assistant" in one day during a hackathon. \\
\hspace{0.1cm} $\bullet$\hspace{0.05cm} Designed a calculator to assist students in learning calculus by providing an easy-to-use GUI interface created by \textbf{Java's} Swing Framework.\\ 
\hspace{0.1cm} $\bullet$\hspace{0.05cm} Users can zoom in and zoom out easily. A quiz mode was also developed to enhance their learning experience.

\textbf{Incubator program} \hfill \href{https://youtu.be/gJmWtfJp0Yc?t=345}{Link to Incubator Kick-off}\\
\textit{January - Present, 2023}\\
\hspace{0.1cm} $\bullet$ \hspace{0.04cm}Currently organizing and executing the Incubator program as a logistics team member, helping over 100 participants complete their projects for the \textbf{2023 Google Solutions Challenge}. \\
\hspace{0.1cm} $\bullet$ \hspace{0.1cm}Pairing each participating team with a mentor, organizing workshops to assist the participants to complete their projects, and creating a 9-week plan to guide their progress. \\ 
\hspace{0.1cm} $\bullet$ \hspace{0.1cm}Delivered a 10-minute presentation at the opening ceremony of the Incubator program for over 50 participants. 

\textbf{Personal website} \hfill \href{https://www.zicheng-li.com/}{Link to Website} \\
\textit{January, 2023} \\ 
\hspace{0.1cm} $\bullet$\hspace{0.1cm} Designed and developed a personal website using \textbf{HTML} and \textbf{CSS}, and successfully deployed it on \textbf{AWS Cloud}.

\textbf{Spy Network} \hfill \href{https://github.com/Zicheng-Li/Spy_Network_Framework}{Link to GitHub} \\
\textit{November, 2022} \\
\hspace{0.1cm} $\bullet$ Participated in a spy network project utilizing a combination of \textbf{design patterns} including the Observer pattern, Strategy pattern, Singleton pattern, and Decorator pattern.\\
\hspace{0.1cm} $\bullet$ The purpose of this network is to propagate encryption schemes, allowing spies to communicate securely with one another. Please refer to GitHub for more details.

\textbf{Connect Four}  \hfill \href{https://github.com/Zicheng-Li/Connect_Four}{Link to GitHub} \\
\textit{October, 2022} \\ 
\hspace{0.1cm} $\bullet$ Developed a Connect Four game in \textbf{Java}, offering players the choice to play against one another or an AI opponent. This game also allows you to watch an AI versus AI match.


\section{Work Experience}
\textbf{Incubator Team}  \hfill   October 2021 - present \\
\textit{Google Developer Student Clubs McMaster U}
\\\\\hspace{0.1cm} $\bullet$ Managed logistics for various events, including determining event platforms, outlining event activities, planning in-person social events, and booking activity lounge spaces. \\ 
\hspace{0.1cm} $\bullet$ \hspace{0.05cm}Collaborated with the Marketing team to create a participant handbook, emphasizing effective communication skills.\\
\hspace{0.1cm} $\bullet$ \hspace{0.03cm}Demonstrated leadership skills by holding weekly meetings with the administrative team and reported progress to the Vice President.\\\\
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Street Market Vendor} &  \hfill \normalsize{May 2020 - September 2021} \\
\multicolumn{2}{@{}X@{}}{\textit{ldeas lnc.}}
\end{tabularx} \\\\
\hspace{0.1cm} $\bullet$ Communicated and explained the features of the vendor's products and helped customers find their favourite products.\\
\hspace{0.1cm} $\bullet$ Assisted customers to complete their payments which involved customer service skills.

\section{Achievements}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Faculty of Engineering Award of Excellence Scholarship} & \hfill April 2021 \\
\multicolumn{2}{@{}X@{}}{Awarded the scholarship for enrolling with a high school average of 95\%.}
\end{tabularx}

\section{References}
References available upon request
\end{document}
